Delayed effects of [responses to?] climate lead to demographic divergence in a fragmented Amazonian landscape

### 2021-04-06 doc/paper.Rmd
switch to four-panel plot for size covariate with size distribution at bottom.

```{r load-targets}
withr::with_dir(here(), {
  tar_load(c(
    normals_plot,
    eda_plot,
    s_covar_plot,
    s_spei_plot,
    s_spei_diff_plot,
    g_covar_plot,
    g_spei_plot,
    g_spei_diff_plot,
    f_covar_plot,
    f_spei_plot,
    f_spei_diff_plot
  ))
})
```

@@

```{r}
cap <- "Smooth effect of plant size in the previous census on survival modeled by a cubic regression spline.  95% confidence intervals are shown and include uncertainty in the model intercept and uncertainty due to smoothness selection. The smooths for 1-ha fragments and continuous forest are fit in separate models. The model intercepts were added to the fitted values of the smooth and values are back-transformed to the response scale"
```

```{r surv-size, fig.cap=cap}
s_covar_plot
```

@@

Log transformed plant size had a significant effect on survival in both continuous forest and 1-ha fragments (both p \< 0.001).
Survival probability of large plants approached 1 in both habitat types (Figure \@ref(fig:surv-size)).
Survival of the smallest plants was higher in 1-ha fragments, but the 95% confidence intervals for 1-ha fragments and continuous forest overlapped for all sizes.

@@

```{r}
cap <- "Smooth effect of plant size in year t on plant size in year t+1 modeled by a cubic regression spline.  95% confidence intervals are shown and include uncertainty in the model intercept as well as uncertainty due to smoothness selection. The dashed red line represents a 1:1 line for reference. The smooths for 1-ha fragments and continuous forest are fit in separate models. Model intercepts were added to the fitted values of the smooths."
```

```{r growth-size, fig.cap=cap}
g_covar_plot
```

@@

Size in year t was a significant predictor of size in year t+1 (p \< 0.001).
The 95% confidence intervals for the effect of size in year t in fragments and continuous forest overlapped for most sizes, but was slightly higher in continuous forest for mid-sized plants (Figure \@ref(fig:growth-size)).

@@

```{r}
cap <- "Smooth effect of plant size in the previous census on flowering probability modeled by a cubic regression spline.  95% confidence intervals are shown and include uncertainty in the model intercept as well as uncertainty due to smoothness selection. The smooths for 1-ha fragments and continuous forest are fit in separate models. The model intercepts were added to the fitted values of the smooth and values are back-transformed to the response scale"
```

```{r flwr-size, fig.cap=cap}
f_covar_plot
```

<!--# instead of rug plot, add second panel or margin with box plots or violin plots of size at both habitats -->

Plant size had a significant effect on flowering probability in both habitats (p \< 0.001).
Flowering probability increased rapidly with log-transformed plant size greater than 5 in both habitats (Figure \@ref(fig:flwr-size)).
Flowering probability of large plants (log(size) \> 5) was greater in 1-ha fragments compared to continuous forest.
However, because mean plant size is larger in continuous forest, overall flowering probability was greater.
<!--# idea: plot vertical lines representing mean or median size in each habitat -->

@@

#### Vocab

Delayed effects, time lag, the lag...avoid lagged effects

>>>>

```{r load-targets}
withr::with_dir(here(), {
  tar_load(c(
    normals_plot,
    eda_plot,
    s_spei_plot,
    s_spei_diff_plot,
    g_spei_plot,
    g_spei_diff_plot,
    f_spei_plot,
    f_spei_diff_plot,
    size_plot
  ))
})
```

@@

```{r}
cap <- "Smooth effect of plant size in the previous census on a) survival, b) log(size), and c) flowering probabiility, modeled by a cubic regression splines. Panel d) shows the smoothed density of different plant sizes in the two habitat types. 95% confidence intervals are shown and include uncertainty in the model intercept and uncertainty due to smoothness selection. The smooths for 1-ha fragments and continuous forest are fit in separate models. The model intercepts were added to the fitted values of the smooth and values are back-transformed to the response scale.  In b), a 1:1 line is shown in dashed red to indicate the line of no growth."
```

```{r size-plot, fig.cap=cap, fig.height=8, fig.width=5}
size_plot
```

@@

Log transformed plant size had a significant effect on survival in both continuous forest and 1-ha fragments (both p \< 0.001).
Survival probability of large plants approached 1 in both habitat types (Figure \@ref(fig:size-plot)a).
Survival of the smallest plants was higher in 1-ha fragments, but the 95% confidence intervals for 1-ha fragments and continuous forest overlapped for all sizes.

@@

@@

Size in year t was a significant predictor of size in year t+1 (p \< 0.001).
The 95% confidence intervals for the effect of size in year t in fragments and continuous forest overlapped for most sizes, but was slightly higher in continuous forest for mid-sized plants (Figure \@ref(fig:size-plot)b).

@@

Plant size had a significant effect on flowering probability in both habitats (p \< 0.001).
Flowering probability increased rapidly with log-transformed plant size greater than 5 in both habitats (Figure \@ref(fig:size-plot)c).
Flowering probability of large plants (log(size) \> 5) was greater in 1-ha fragments compared to continuous forest.
However, because mean plant size is larger in continuous forest (Figure \@ref(fig:size-plot)d), overall flowering probability was greater.

@@
